\vspace{3cm} \Huge{\futhark}\\ \Large{Enhancing performance by rewriting kernels from Python/OpenCL to Futhark}

### 2017-11-09 report/draft.tex
k

  \begin{mdframed}[
    frametitle={Why does Futhark perform faster than OpenCL?},
    nobreak=true]
While it was expected to see Futhark outperform the strictly CPU based 
computations performed by Numpy in the Python models, it was more uncertain
how much (or even whether) Futhark would outperform OpenCL.

@@

However, when we work with the rewritten core shell parallelepiped, we see huge
speedups even at n=100. This speedup mainly comes from Futharks ## INDSÆT DET 
DER FEDE NOGET MED MAPS.
Looking at the definition of core_shell_parallelepiped_futhark, we see that 11
parameters are extracted from the local\_values array. We could fear that this
happens for every application of Iq, but the Futhark compiler actually performs
HOISTING, which is an optimization that rewrites the program internally, so that
these variable allocations are moved out of the Iq function, and are thus only
performed once, instead of n times.
# KIIIIIIIIIILDE

>>>>

\begin{mdframed}[
    frametitle={Why does Futhark perform faster than OpenCL?},
    nobreak=true]

While it was expected to see Futhark outperform the strictly CPU based 
computations performed by Numpy in the Python models, it was more uncertain
how much (or even whether) Futhark would outperform OpenCL.

@@

However, when we work with the rewritten core shell parallelepiped, we see huge
speedups even at n=100. This speedup mainly comes from Futharks ## INDSÆT DET 
DER FEDE NOGET MED MAPS.
Looking at the definition of core_shell_parallelepiped_futhark, we see that 11
parameters are extracted from the local\_values array. We could fear that this
happens for every application of Iq, but the Futhark compiler actually performs
HOISTING, which is an optimization that rewrites the program internally, so that
these variable allocations are moved out of the Iq function, and are thus only
performed once, instead of n times.
# KIIIIIIIIIILDE
\end{mdframed}
